(1) Homework Assignments – discuss whether you thought the homework assignments were good learning tools for SE3303.
Homework assignments were appropriately positioned throughout the term to test and reinforce lectues, readings, and other class materials.  I felt that the homework assignments specifically provided a good springboard to solid performance on the Projects and final exam.

(2) Discussion Board Assignments – discuss whether you thought the DBs were good learning tools for SE3303.  
The discussion board assignments helped significantly to close the loop with regard to the group projects.  I took the time to read through the posts from my other group members after each group project and tried to internalize the feedback in order to make each successive project work more smoothly.

(3) Project – discuss whether you thought the project was a good learning tool for SE3303. Was it useful to work in groups?
Working in groups was integral to this course and helped facilitate mastery of the material.  The group interaction helped me to identify areas where my understanding was less than throrough.  Furthermore, knowing that my group was counting on me to carry my share of the load held me accountable to the extra readings which I might otherwise have skipped over.

(4) Discuss your favorite topic that we studied this semester—why was it your favorite suitability topic?
While I found all of the material in this class interesting and relevant, CAIV analysis provided the most interest to me.  Since my background is in mathematics as well as computer science, I really liked the objectification of decision making provided by this analysis technique.  As a systems engineer, I like being able to point to verifiable and quantifiable (demonstrable) data to support decisions.

(5) Any other feedback for SE3303?
I appreciate your decision to forgo the last report in favor of having a final exam.  While the workload for this class was not inordinately heavy, coupled with the demands of the other class it would have been difficult to manage an adequate effort in both.
