\documentclass[letterpaper,10pt]{article}

%\setlength{\parindent}{0in}
%\usepackage{fullpage} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage[table]{xcolor}
\usepackage{dcolumn}
\oddsidemargin 0.0in
\textwidth 6.5in
\newcolumntype{.}{D{.}{.}{-1}}
\newcommand*{\myalign}[2]{\multicolumn{1}{#1}{#2}}
\usepackage{lastpage} % for the number of the last page in the document
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\lfoot{Project Team 5 (Gildea, Mazza, Peters): Assignment 8}
\rfoot{Page \thepage\ of \pageref{LastPage}}

%opening
\title{Kitchen and Patio Renovation}
\author{Project Team 5 \\ { \small (Gregg Gildea, Steve Mazza, Brent Peters)}}
\date{June 8, 2012}

\begin{document}
\maketitle

We feel that the following proposal satisfies the majority of the homeowner's needs and falls under the proposed budget by \$395.37.

\section*{Total Cost \dotfill\$29,604.63}

\section{Appliances\dotfill\$5,979.63}
\emph{Time: 4 hours} \\
The following assumes the acceptance of consumer-grade stainless steel appliances similar to those commonly available from the big box stores.

\subsection{Dishwasher\dotfill\$1,052.31}
\emph{Time: 4 hours} \\
Maytag Model \#MDB8959SAS
	\begin{itemize}
		\item cost\dotfill \$764.10 
		\item tax\dotfill \$38.02 
		\item installation\dotfill \$250.00 
	\end{itemize}
\subsection{Ovens\dotfill\$2,639.06}
\emph{Time: 4 hours} \\
Selecting an electric double oven results in far more consumer choices and much better prices even after factoring in the cost of new electric service.\\
Maytag Model \#WOD51EC0AS  (30`` electric)
	\begin{itemize}
		\item cost\dotfill\$1,799.10
		\item tax\dotfill\$89.96
		\item electric service\dotfill\$300.00
		\item cabinet filler\dotfill\$200.00
		\item installation\dotfill\$250.00
	\end{itemize}
\subsection{Cooktop\dotfill\$1,146.81}
\emph{Time: 4 hours} \\
Frigidaire Model \#FGGC3645KS
	\begin{itemize}
		\item cost\dotfill\$854.10
		\item tax\dotfill\$42.71
		\item installation\dotfill\$250.00
	\end{itemize}
\subsection{Vent Hood\dotfill\$1,141.45}
\emph{Time: 4 hours} \\
Cavaliere-Euro Model \#SV218DI36
	\begin{itemize}
		\item cost\dotfill\$849.00
		\item tax\dotfill\$2.45
		\item installation\dotfill\$250.00
	\end{itemize}

\section{Demolition\dotfill\$1,500.00}
\emph{Time: 1 day, initially} \\
This item covers all demolition, disposal, trash removal, and clean-up necessary on the entire job.

\section{Paint\dotfill\$800.00}
\emph{Time: 2 days, divided} \\
Prep, primer, and 2 coats of single color flat latex interior paint for all affected surfaces.

\section{Trim\dotfill\$800.00}
\emph{Time: 4 hours} \\
All trim carpentry work necessary to replace baseboard and casement moldings throughout the work area.  Covers material and labor.

\section{Counters\dotfill\$6,725.00}
\emph{Time: 1.5 days, divided (half day, initially, for measuring} \\
Manufactured solid surface counter top (e.g., Corian) based on 54.5 linear feet at \$150/lft.  Price includes material and labor but may vary based on availability and selection.  This assumes the homeowner will keep the existing cabinet/counter top layout.

\section{Cabinet Re-facing\dotfill\$5,000.00}
\emph{Time: 3 days, not counting lead time for delivery} \\
This is an economical way to re-use existing cabinets.  Doors and hardware will be replaced and frames will be re-finished.  Includes minor repair to existing frames.  The result should appear as new at about half the cost of total replacement.  This assumes the homeowner will keep the existing cabinet/counter top layout.

\section{Hardwood Flooring\dotfill\$1,200.00}
\emph{Time: 2 days, divided} \\
Sand and re-finish existing hardwood flooring.  Estimate is based on $10\times20$ foot area (including waste) at \$6.00 per sqft.  

\section{Plumbing\dotfill\$900.00}
\emph{Time: 8 hours, divided} \\
Assumes that new fixtures of the same size will replace existing in the same location.  Covers material and labor.  Price may vary based on selection and availability.
\begin{itemize}
	\item Remove two sinks and cap service \dotfill\$250.00
	\item Adjust rough-in as necessary \dotfill\$150.00
	\item Install new sinks and faucets \dotfill\$500.00
\end{itemize}

\section{Electrical\dotfill\$0.00}
\emph{Time: 0 hours} \\
All electrical work is covered under installation line items for each appliance.  Assumes that no replacement or relocation will be necessary for any existing fixtures.  Also assumes no new service from the panel.

\section{Furniture\dotfill\$900.00}
\emph{Time: 0 hours}
Provide six (6) new bar stools for the kitchen island at a cost of \$150.00 each.  Price may vary based on customer selection.

\section{Patio\dotfill\$5,800.00}
\emph{Time: 3 days} \\
Improvements will include a privacy fence in line with the neighbor's field of view, planters, plants, furniture, and miscellaneous repairs as necessary.  Also, the patio will be pressure washed.  A custom ledge will be constructed outside the existing kitchen window to act as a serving ledge.  Items can be passed through from the kitchen to the patio without walking around to the sliding door.
\begin{enumerate}
	\item Pressure wash patio\dotfill\$250.00
	\item Privacy fence with arbor\dotfill\$2,400.00
	\item Custom planters to match\dotfill\$800.00
	\item Serving Pass-through\dotfill\$750.00
	\item Plants\dotfill\$400.00
	\item Patio furniture\dotfill\$1,200.00
\end{enumerate}

\section*{Sequence of Jobs}
This is the optimal arrangement of the jobs.  It prevents delays and keeps subcontractors from working on top of each other.\\
\\
Items in \textcolor{red}{red} should not be moved.  These are also \emph{serial} tasks.\\
Items in \textcolor{blue}{blue} can be completed at any time.\\
Look for items that can be performed in parallel.  Assume a working crew of three (3) comprised of one (1) skilled carpenter, one (1) journeyman, and one (1) laborer.  Countertops will be installed by the vendor and plumbing is sub-contracted out.
\begin{enumerate}
\item\textcolor{red}{Remove fixtures, sinks and cap service\dotfill 4 hours}
\item \textcolor{red}{Principal demolition\dotfill 1 day}
\item \textcolor{red}{Strip hardwood flooring\dotfill 1 day}
\item Apply three (3) coats polyurethane gloss finish to floors\dotfill 1 day
\item Prep cabinet frames\dotfill 1 day
\item Re-finish cabinet frames\dotfill 4 hours
\item Measure for new countertops\dotfill 4 hours
\item Match, repair, and install baseboard, quarter-round, and other moldings\dotfill 4 hours
\item Caulk and apply primer to all paintable surfaces\dotfill 6 hours
\item Apply two (2) coats interior latex paint to all paintable surfaces\dotfill 1 day
\item Finish new cabinet doors\dotfill 6 hours
\item Install new cabinet doors\dotfill 2 hours
\item Install new cabinet hardware\dotfill 3 hours
\item \textcolor{red}{Install new countertops\dotfill 1 day}
\item \textcolor{red}{Install new fixtures, sinks\dotfill 4 hours}
\item \textcolor{red}{Appliance installation\dotfill 2 days}
\item \textcolor{blue}{Pressure wash patio\dotfill 2 hours}
\item \textcolor{blue}{Construct privacy fence with arbor\dotfill 8 hours}
\item \textcolor{blue}{Construct custom planters\dotfill 6 hours}
\item \textcolor{blue}{Construct ledge for pass-through\dotfill 2 hours}
\item Assemble furniture and plants\dotfill 4 hours
\end{enumerate}

\end{document}