\documentclass[letterpaper,12pt]{article}

%\setlength{\parindent}{0in}
%\usepackage{fullpage} 
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{enumerate}
\usepackage{graphicx}
\usepackage[table]{xcolor}
\usepackage{dcolumn}
\usepackage[english]{babel}
\oddsidemargin 0.0in
\textwidth 6.5in
\newcolumntype{.}{D{.}{.}{-1}}
\newcommand*{\myalign}[2]{\multicolumn{1}{#1}{#2}}
% Alter some LaTeX defaults for better treatment of figures:
% See p.105 of "TeX Unbound" for suggested values.
% See pp. 199-200 of Lamport's "LaTeX" book for details.
%   General parameters, for ALL pages:
\renewcommand{\topfraction}{0.9}	% max fraction of floats at top
\renewcommand{\bottomfraction}{0.8}	% max fraction of floats at bottom
%   Parameters for TEXT pages (not float pages):
\setcounter{topnumber}{2}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{4}     % 2 may work better
\setcounter{dbltopnumber}{2}    % for 2-column pages
\renewcommand{\dbltopfraction}{0.9}	% fit big float above 2-col. text
\renewcommand{\textfraction}{0.07}	% allow minimal text w. figs
%   Parameters for FLOAT pages (not text pages):
\renewcommand{\floatpagefraction}{0.7}	% require fuller float pages
% N.B.: floatpagefraction MUST be less than topfraction !!
\renewcommand{\dblfloatpagefraction}{0.7}	% require fuller float pages


\title{Group Presentation Reviews \\ \large Group 4}
\author{Douglas Brown \\ Jessica Hale \\ Steve Mazza \\ Daniel Torres}
\date{February 22, 2012}

\begin{document}
\maketitle

All presenters did really well.  We were impressed with the thorough understanding exhibited by all speakers and the manner in which the results were presented.  Though everyone performed highly, we were most impressed with Group 6.  The enclosed comments may, at times, be nit-picky and are not in any way meant to denigrate the obvious hard efforts of the teams. Our opinions are presented at your request and are intended solely for your personal use and are not intended for redistribution. 

\section*{Group 5}
  \begin{itemize}
    \item The background noise that was present throughout the presentation was somewhat distracting.
	\item On slide 2 it was not clear what supporting graphic was being referred to during the talk. It would have been easier to follow if they were allowed to break this slide out into several others.
	\item Slide 3 had a very clear supporting graphic. 
	\item Slide 4 was also very well organized and presented clearly. Tabular data supported discussion. 
	\item Summary was clear and ended with a single conclusion. 
	\item Timing was adequate. 
	\item Presentation sounded well rehearsed.
  \end{itemize}

\section*{Group 2}
\begin{itemize}
  \item Content on the slides matched the soundtrack almost too well.
  \item Lots of words on the slides made the message of each slide less clear.
  \item Graphic on slide 2 was effective.
  \item 4 identical graphics on slide 3 took up a lot of space and lent little to the discussion.
  \item Extremely busy graphic in slide 4 showing how the rail gun works seemed out if place in this presentation.
  \item Timing was adequate.
\end{itemize}

\section*{Group 6}
\begin{itemize}
  \item Seemed well rehearsed.
  \item Introduction was clear and they asked up front for a decision.
  \item Presentation of decision criteria was clear.
  \item Use of graphics was effective and statistics were summarized in the discussion.
  \item Out of the box thinking to add a 3-gun system for consideration.
  \item Clear recommendation at the conclusion.
\end{itemize}

\section*{Group 1}
\begin{itemize}
  \item Group 1 had the most comprehensive analysis, thorough justification of the results and recommendations, and explanation of assumptions - but the data is meant to be spread across about 15 slides and the brief required a half hour.      
  \item Slide 1 is extremely full and the data is overwhelming. 
  \item Christine was clearly well rehearsed and presented well. 
  \item Defined success and failure criteria instead of assuming 100\% success rate (good). 
  \item Slide 2 contains way too much raw data. 
  \item Analysis on slide 3 was good. Summary is clear.
\end{itemize}

\end{document}
